Robertson and Cao Project

### 2024-04-04 products/manuscript/Manuscript.qmd
Images and Summary Table
Fixed images in manuscript and added summary table in EDA (work in progress).

We use our exploratory analysis to determine the distribution of our predictors, including the socioeconomic variables that we chose for analysis.
The distribution of the numerical income to poverty ratio can be shown below.
It displays a value from 1-3.
A ratio displaying less than 1 depicts an income less than the poverty level.Any income ratio \>1 indicates an income greater than the poverty level.
Most of the observations were gathered from households with income ratios of 3, as shown by the skewed plot below.

![Figure 1. Income-poverty ratio distribution](../results/figures/income.png)

Nest, the distribution of surveys given per state was analyzed.
The state variable shows a more uniformed distribution, suggesting that the observations were gathered fairly across the US states and territory.
Although it is noted a few territories provides 0 observations.
![Figure 2. State dsitribution](results/figures/state_distribution.png)

The family income variable provides a more normal distribution with the majority of the observation coming from \$75000+ income level.
![Figure 3. The family income distribution](results/figures/family.income.distribution.png)

@@

![Figure 4.Racial distribution](results/figures/race.distribution.png) ![Figure 5.Ethnicity distribution](results/figures/ethnicity.distribution.png)

The Insurance status variable shows that the majority of the observations came from households with private insurance only.
This is followed by any medicaid and then other insurance.
This is mirrored in the facility variable, where a majority of its observations show private facilities being the location.
![Figure 6. Insurance status distribution](results/figures/insurance.status.distribution.png) ![Figure 7. Distribution of the medical facility where the survey was administerred](results/figures/facility.distribution.png)

@@

![Figure 8. Vaccine status distribution](../results/figures/State-vaccine-completion.png)

@@

![Figure 9.Facility and vaccine completion distribution](results/figures/facility-vaccination.png)

@@

![Figure 10. Distribution of vaccine completion stratified by race and ethnicity](results/figures/race-ethnicity-vaccination.png)

@@

![Figure 11.](figures/results/income-vaccination.png)

@@

![Figure 12. Income poverty ratio and insurance status](results/figures/insurance-income-stratified.png)

@@

![Figure 14. Income-poverty level versus ethnic group](results/figures/raceeth-income-stratified.png)

{{< pagebreak >}} \# Analysis

>>>>

We use our exploratory analysis to determine the distribution of our predictors, including the socioeconomic variables that we chose for analysis.
The overall distribution of each factor variable is shown below.
![Table 1.]
The distribution of the numerical income to poverty ratio can be shown below.
It displays a value from 1-3.
A ratio displaying less than 1 depicts an income less than the poverty level.Any income ratio \>1 indicates an income greater than the poverty level.
Most of the observations were gathered from households with income ratios of 3, as shown by the skewed plot below.

![Figure 1. Income-poverty ratio distribution](./images/income.png)

Nest, the distribution of surveys given per state was analyzed.
The state variable shows a more uniformed distribution, suggesting that the observations were gathered fairly across the US states and territory.
Although it is noted a few territories provides 0 observations.
![Figure 2. State distribution](./images/state.distribution.png)

The family income variable provides a more normal distribution with the majority of the observation coming from \$75000+ income level.
![Figure 3. The family income distribution](./images/family.income.distribution.png)

@@

![Figure 4.Racial distribution](./images/race.distribution.png)

![Figure 5.Ethnicity distribution](./images/ethnicity.distribution.png)

The Insurance status variable shows that the majority of the observations came from households with private insurance only.
This is followed by any medicaid and then other insurance.
This is mirrored in the facility variable, where a majority of its observations show private facilities being the location.
![Figure 6. Insurance status distribution](./images/insurance.status.distribution.png) ![Figure 7. Distribution of the medical facility where the survey was administerred](./images/facility.distribution.png)

@@

![Table 2. Vaccine status distribution](./images/state-vaccine-completion.png)

@@

![Figure 8.Facility and vaccine completion distribution](./images/facility-vaccination.png)

@@

![Figure 9. Distribution of vaccine completion stratified by race and ethnicity](./images/raceeth-income-stratified.png)

@@

![Figure 10.](./images/income-vaccination.png)

@@

![Figure 11. Income poverty ratio and insurance status](./images/insurance-income-stratified.png)

@@

![Figure 12. Income-poverty level versus ethnic group](./images/raceeth-income-stratified.png)

# Analysis
